---
title: "R Notebook"
output: html_notebook
---

#### Authors: Martin Ostrowski, Deepa Varkey and Mark Brown
#### Date: 20190418
#### email: martin.ostrowski@uts.edu.au

This workbook details the extraction of CARS data from nedtcdf format to Long format

CARS weekly and CARS global monthly data was downloaded from the [AODN portal](https://portal.aodn.org.au) as .nc files
Bathymetry data was extracted from the GEBCO grid. 

1. Processing CARS weekly

```{r}
library(ncdf4)
library(tidyverse)
library(oce)
library(shapefiles)
library(rgdal)
```

Extract the data from relevant variables 
```{r}
carsw<-nc_open('~/downloads/IMOS_aggregation_20190529T011708Z/IMOS_aggregation_20190529T011708Z.nc')


clat<-ncvar_get(carsw, "LATITUDE")
clon<-ncvar_get(carsw, "LONGITUDE")
cday<-ncvar_get(carsw, "DAY_OF_YEAR")
cdepth<-ncvar_get(carsw, "DEPTH")
ctemp<-ncvar_get(carsw, "TEMP")
csal<-ncvar_get(carsw, "PSAL")
cdox2<-ncvar_get(carsw, "DOX2")
cntr<-ncvar_get(carsw, "NTR2")
csil<-ncvar_get(carsw, "SLC2")
cpho<-ncvar_get(carsw, "PHOS")


myvals<-c("lat", 'lon', 'day', 'depth','temp', 'sal', 'silicate','o2', 'N', 'P')

````

establish the dimensions of the data frames for each day
  
```{r}
ndays<-length(cday)
nlats<-length(clat)
nlons<-length(clon)
my.depth=0
```
Create a list of dfs and use a loop to extract each variable, converting from a matrix to a vector

then join all of the dfs using bind_rows and derive n.p, nstar and join the bottom_depth from the 0.5 degree extracted bathymetry. 

Add day length and see below for code to plot the data for error checking.

### Check n.p, nstar for dodgy values

set a cleiling of 100 for n.p and nstar

```{r}
cars.weekly<-vector('list', length=ndays)

cars.weekly[[1]]<-data.frame(matrix(ncol=length(myvals), nrow=length(as.vector(ctemp[,,1,cday[1]]))))

clats<-rep(clat[1], length(clon))
for (i in 2:length(clat)){
clats <- c(clats, rep(clat[i], length(clon)))
}

10695/length(clon)


for (i in 1:52){
  
cars.weekly[[i]]<-data.frame(matrix(ncol=length(myvals), nrow=length(as.vector(ctemp[,,1,cday[1]]))))
colnames(cars.weekly[[i]])<-myvals
cars.weekly[[i]][,1]<-clats
cars.weekly[[i]][,2]<-rep(clon, 93)
cars.weekly[[i]][,3]<-rep(cday[i], 10695)
cars.weekly[[i]][,4]<-rep(0, 10695)
cars.weekly[[i]][,5]<-as.vector(ctemp[,,1,i])
cars.weekly[[i]][,6]<-as.vector(csal[,,1,i])
cars.weekly[[i]][,7]<-as.vector(cdox2[,,1,i])
cars.weekly[[i]][,8]<-as.vector(csil[,,1,i])
cars.weekly[[i]][,9]<-as.vector(cntr[,,1,i])
cars.weekly[[i]][,10]<-as.vector(cpho[,,1,i])
}

cars.weekly<-bind_rows(cars.weekly)

cars.weekly$n.p<-cars.weekly$N/cars.weekly$P

cars.weekly$nstar<-ifelse(cars.weekly$N/cars.weekly$P >0, cars.weekly$N/cars.weekly$P, 0)

mybath<-read_csv('~/Dropbox/zOTUs/model.inputs/bathymetry.csv')
lons<-seq(0,360,0.5)
lats<-seq(-90,90, 0.5)

colnames(mybath)<-lons[-1]
mybath$lat<-lats[-1]

mybath.tidy <- mybath %>% gather(key = lon, value='bottom_depth', -lat)

mybath.tidy$lat <- as.numeric(mybath.tidy$lat)
mybath.tidy$lon <- as.numeric(mybath.tidy$lon)
mybath.tidy$lon <- mybath.tidy$lon-180
cars.weekly <- cars.weekly %>% left_join(mybath.tidy, c('lat','lon'))
cars.weekly$strat<-0
cars.weekly$daylength<-daylength(cars.weekly$lat, (cars.weekly$day))*60
write_csv(cars.weekly, '~/Dropbox/zOTUs/model.inputs/cars.weekly.v1.csv')

cars.weekly$n.p[cars.weekly$n.p > 100]<- 100
cars.weekly$nstar[cars.weekly$nstar > 100]<- 100
table(cars.weekly$n.p[cars.weekly$n.p == Inf])
write_csv(cars.weekly, '~/Dropbox/zOTUs/model.inputs/cars.weekly.v1.csv')

```
****


Repeat for CARS annual

```{r}

carsa<-nc_open('~/downloads/IMOS_aggregation_20190529T011611Z/IMOS_aggregation_20190529T011611Z.nc')


alat<-ncvar_get(carsa, "LATITUDE")
alon<-ncvar_get(carsa, "LONGITUDE")
aday<-ncvar_get(carsa, "DAY_OF_YEAR")
adepth<-ncvar_get(carsa, "DEPTH")
atemp<-ncvar_get(carsa, "TEMP")
asal<-ncvar_get(carsa, "PSAL")
adox2<-ncvar_get(carsa, "DOX2")
antr<-ncvar_get(carsa, "NTR2")
asil<-ncvar_get(carsa, "SLC2")
apho<-ncvar_get(carsa, "PHOS")
cars.annual<-vector('list', length=length(aday))

cars.annual[[1]]<-data.frame(matrix(ncol=length(myvals), nrow=length(as.vector(atemp[,,1,aday[1]]))))

alats<-rep(alat[1], length(alon))
for (i in 2:length(alat)){
alats <- c(alats, rep(alat[i], length(alon)))
}

238651/length(alon)


for (i in 1:12){
  
cars.annual[[i]]<-data.frame(matrix(ncol=length(myvals), nrow=238651))
colnames(cars.annual[[i]])<-myvals
cars.annual[[i]][,1]<-alats
cars.annual[[i]][,2]<-rep(alon, 331)
cars.annual[[i]][,3]<-rep(aday[i], 238651)
cars.annual[[i]][,4]<-rep(0, 238651)
cars.annual[[i]][,5]<-as.vector(atemp[,,1,i])
cars.annual[[i]][,6]<-as.vector(asal[,,1,i])
cars.annual[[i]][,7]<-as.vector(adox2[,,1,i])
cars.annual[[i]][,8]<-as.vector(asil[,,1,i])
cars.annual[[i]][,9]<-as.vector(antr[,,1,i])
cars.annual[[i]][,10]<-as.vector(apho[,,1,i])
}

cars.annual[[1]][,1]
head(cars.annual[[1]])
cars.annual<-bind_rows(cars.annual)

cars.annual$n.p<-cars.annual$N/cars.annual$P

cars.annual$nstar<-ifelse(cars.annual$N/cars.annual$P >0, cars.annual$N/cars.annual$P, 0)
mybath.tidy$lon <- mybath.tidy$lon+180
cars.annual <- cars.annual %>% left_join(mybath.tidy, c('lat','lon'))
cars.annual$strat<-0
cars.annual$lon <-ifelse(cars.annual$lon < 180, cars.annual$lon, cars.annual$lon - 360)

cars.annual$daylength<-daylength(cars.annual$lat, (cars.weekly$day))*60
cars.annual$n.p[cars.annual$n.p > 100]<- 100
cars.annual$nstar[cars.annual$nstar > 100]<- 100
table(cars.annual$n.p[cars.annual$n.p == Inf])

write_csv(cars.annual, '~/Dropbox/zOTUs/model.inputs/cars.annual.v1.csv')
```

***

testing below


```{r}

            
ggplot(cars.annual %>%  filter(day==32), aes(x=lon, y=lat, fill=temp)) + geom_tile(na.rm = T)
```

```{r}
ggplot(test %>%  filter(day==1), aes(x=lon, y=lat, fill=N)) + geom_tile(na.rm = T)
```

```{r}
ggplot(cars.annual %>%  filter(day==1), aes(x=lon, y=lat, fill=bottom_depth)) + geom_tile(na.rm = T)
```
```{r}
ggplot(cars.annual %>%  filter(day==1, nstar < 20), aes(x=lon, y=lat, fill=nstar)) + geom_tile(na.rm = T)
```

