---
title: "R Notebook"
output: html_notebook
---

There are several workflows and notes in here. The primary outcome is the development of a process for reading in models from .RDS files

pipelining the predictions for both gaussian and poisson function models

transforming the predictions to matricies and then presenting them as rasters using faceted ggplots

Things to consider: is the data alrready in long format and therefore it is not needed to convert to matrix
error check the preparation of the cars monthly files. In this workflow the monthly data files are imported out of calendar sync (m1, m10, m11, m12, m2 ...

)

```{r}

library(gbm)
library(maps)
library(tidyquant)
library(maptools)
library(shapefiles)
library(rgdal)
library(ggplot2)
library(rgeos)
library(ncdf4)
library(knitr)
library(oce)
```


#### in a parallel workflow we are comparing the two sets of zOTU ids - we are extracting teh ASV species identifications for zOTUs using both green genes, SIlva 132  (which is terrible for marine Cyanobacteria, and probably also for other species as well). 

Process the taxonomic assignment to help annotate the plots and aggregate the data for evaluation of predicted versus real

```{r, results='asis'}

#tax3<-read_csv("~/Dropbox/zOTUs/TZ/amd.b16s.nochim.dada2taxonly.csv")
#tax2<-read_csv("/Volumes/Monkey/Dropbox/zOTUs/TZ/amd.b16s.nochim.dada2tax.csv")
tax4<-read_csv("~/Dropbox/zOTUs/TZ/input/in16t02.seqtab.nochim.taxwAMDID_amdtax.csv")
#tax5<-read_csv("/Volumes/Monkey/Dropbox/zOTUs/TZ/in16t02.seqtab.nochim.taxwAMDID.csv")
in16.tax<-read_csv("~/Dropbox/zOTUs/TZ/input/in16.tax.silva132.cyano.csv")
in16.tax.names<- unite(in16.tax, "plot.name", c("AMD_ID","Family", "Genus", "Species"), sep=" ", remove = F) # plot.name will be used to annotate each plot


kable(in16.tax.names[,-5])
```

```{r, results='asis'}
kable(sar11_top10[,-3])
```



Get the map outlines and fortify for ggplot
```{r}

GlobalCoastline3 <- readShapePoly("/Volumes/Monkey/Dropbox/gshhg-shp-2/GSHHS_shp/l/GSHHS_l_L1.shp") #potentially mediumn resolution

shore3 <- fortify(GlobalCoastline3)

saveRDS(shore3, "fortified_shoreline_ggplot_models.RDS")
```



Direct comparison with global gaussian models - convert all of the models to .rds
```{r}

#d0tz.preds<-matrix('numeric', nrow=nrow(d0tz), ncol=nrow(gmods.rds.names))
#d0tz.preds<-read_csv("/Volumes/Monkey/Dropbox/zOTUs/TZ/d0tz.pres.csv") # predictions so far

#d0tz<-d0cars.new %>% filter (lat > -55, lat< 0, lon > 90)
d0tz<-read_csv("/Volumes/Monkey/Dropbox/zOTUs/TZ/d0tz.csv")

d0tz$month.abb<-as.factor(d0tz$month.abb)
d0tz$month.abb<-factor(d0tz$month.abb, levels=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))


action.run.these<-read_csv("~/Dropbox/zOTUs/TZ/input/run.list.csv")

action.run.these.test<- action.run.these %>% 
  dplyr::group_by(AMD_ID) %>% 
  dplyr::mutate(sum = sum(temp.x))

names.d0tz.preds.3<-vector('double', nrow(action.run.these))
d0tz.preds.3<-matrix(-9999, nrow=nrow(d0tz), ncol=nrow(action.run.these))
#for (i in seq_along(gmods.rds.names$value)){
n=1
#for (n in seq_along(action.run.these)){
for (n in 51:100){
setwd('/Volumes/LaCie/BRT_2018/tz_models_210618_DRV/')  
mod<-readRDS(paste(action.run.these$ntmp[n]))
names.d0tz.preds.3[n]<-mod[[28]][[5]]
tmp<-predict.gbm(mod, d0tz, n.trees=mod[[28]][[15]], type="response")
d0tz.preds.3[,n]<-tmp^2
temp<-cbind(d0tz[,c(1:3, 13)], as.numeric(d0tz.preds.3[,n]))
colnames(temp)[5]<-"abundance"

#generate a plot to check the sanity of the prediction and double check that the model names match!!

ggplot(temp, aes(x = lon, y = lat, fill = abundance))  + ylim(-55,0) + xlim(90,180) +
    labs( x= "Longitude (˚E)", y="Latitude (˚N)", title = paste(action.run.these$plot.name[[n]], sep="")) +
    geom_raster(interpolate = TRUE) +
    scale_fill_gradientn(colours = c("white", rev(oceColorsTemperature(1026))), na.value = NA) +
    geom_polygon(data = shore3, aes(x=long, y = lat, group = group), color = "NA", fill = "grey80") +
    theme_bw() +
    coord_fixed(1.3) +
    facet_wrap(. ~ month.abb) + theme_tq() + theme(panel.spacing = unit(0.05, "cm")) +theme(legend.position="right")
ggsave(filename =paste("/Volumes/Monkey/",names.d0tz.preds.3[[n]], ".g.local.pdf", sep=""))
}
```
#

```{r}

export<-d0tz.preds.3[,21:50]
colnames(export)<-names.d0tz.preds.3[21:50]

export.table<-cbind(d0tz, export)
write_csv(as.data.frame(export), "/Volumes/Monkey/Dropbox/zOTUs/TZ/tz.models.progress.21.50.csv")


```

read-in the prediction data, rbind the real and predicted after working out the intersect between column names =zOTUS. (and find a way to do this with tidyverse ==> this is now done - see below)

```{r}

#first50names<-unite(first.50.preds, "uniq_ID", c("lat", "lon", "month"), sep="_", remove = F)
first50names.l154<-first50names %>%filter(lon==154, lat >-55, lat<-30, month>7, month<10)
first50names.l154 <- first50names.l154[,c(1,2,4,15:62)]

#get the real data into shape for a rbind

action.run.these.test<-action.run.these.test %>%
  distinct(AMD_ID, .keep_all=T)

run.list<-as.tibble(action.run.these.test)

real.data<-tax4[tax4$X1 %in% run.list$seqs.y,]
in16.real.data<-real.data[,1:31]
in16.real.data.ids <- in16.real.data %>% inner_join(run.list, by=c("X1"="seqs.y"))
in16.real.data.ids.t<-t(in16.real.data.ids[,c(2:31)])
colnames(in16.real.data.ids.t)<-in16.real.data.ids$X1
colnames(in16.real.data.ids.t)<-run.list$AMD_ID[match(colnames(in16.real.data.ids.t), run.list$seqs.y)]
in16.real.data.ids.t<-as.data.frame(in16.real.data.ids.t)
in16.real.data.ids.t$uniq_ID<-row.names(in16.real.data.ids.t)

test<-in16.real.data.ids.t[, colnames(first50names.l154)[colnames(first50names.l154)%in% colnames(in16.real.data.ids.t)]]
test2<-first50names.l154[, colnames(test)]


my.data<-rbind(test,test2) # now rbind the data

#play with the values options
my.data.mod<-my.data
#my.data.mod$AMD_B16Sv1_3_zOTU_673020<-my.data.mod$AMD_B16Sv1_3_zOTU_673020/2
#my.data.mod[31:228,1]<-my.data.mod[31:228,1]/2

```


```{r, fig.width=14, fig.height=6}

barplot(as.matrix(t(sweep(my.data.mod[,-1], 1, rowSums(my.data.mod[,-1]), "/"))), col=rev(mycol), border=NA, las=2, ylim=c(0,1.4), width=c(rep(10,30), rep(2,1018)))
legend("top", run.list$plot.name[match(colnames(my.data)[-1],run.list$AMD_ID)], fill=rev(mycol), ncol=3, cex=1.2)

```

Work up with tidyverse long format and ggplot

1. plot the predictions for visual inspection
2. combine the real and predicted
```{r}
#library(ggpubr)

first.50.preds<-read_csv("/Volumes/Monkey/Dropbox/zOTUs/TZ/output/tz.models.progress.1_50.csv")
first.50.preds$month.abb<-as.factor(first.50.preds$month.abb)
first.50.preds$month.abb<-factor(first.50.preds$month.abb, levels=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "real data","Sep", "Oct", "Nov", "Dec"))

first50preds.l154<-first.50.preds %>%
  filter(lon==154, lat > -55, lat < -30) %>%#subset to the lat and lon range we want
  gather(zOTU, value,  c(14:61)) # convert to long format
#first50preds.l154

#gtest$value<-sqrt(gtest$value)

#plot the monthly predicted communities 
  p3<-ggbarplot(gtest, x= "lat", y = "value",  color = NA,  fill = "zOTU", palette=mycol320,  size = 0.6, alpha = 1,legend = "right", orientation = "vertical")+ #position = position_dodge(1)
    font("xlab", size = 12, color = "blue")+ 
    facet_wrap(. ~ month, drop=T, scales="free", nrow  =4)+ #scales="free"
   #facet_grid(cluster ~ loc, drop=T, scales="free") +
    font("ylab", size = 12, color = "#993333") +
    font("xy.text", size = 3, color = "black") +
    
    theme_tq() +theme(panel.spacing = unit(0.05, "cm"), legend.text=element_text(size=2), 
        legend.key.size = unit(.05, "cm")) + rotate_x_text(45) + scale_x_discrete()
  
  p3 + scale_x_discrete(breaks=seq(-50,0,10), labels=c(-50,-40,-30,-20,-10,0))
  
  ggsave(filename =paste("~/tzline.preds.170.pdf", sep=""), width = 10, height=10)

```

NOw add the lat-lon-month to the in16 real data
```{r, fig.width=10}


in16.coords<-read_csv("/Volumes/Monkey/Dropbox/zOTUs/TZ/in16.sites.cvs") # get the lat lons

in16.real.data.ids.t<-as.data.frame(in16.real.data.ids.t) # get the real data subsetted for zOTUS in the predictions (or not)

in16.real.data.ids.t$uniq_ID<-rownames(in16.real.data.ids.t)

in16.real.data.ids.t<-in16.real.data.ids.t[,-307]
in16.rdg<-in16.real.data.ids.t %>% 
  gather(zOTU, value, -uniq_ID)   %>% # convert to long format and put the columns in order in the next few steps
  mutate(month.abb="real data") %>% #add a month
  inner_join(in16.coords, by=c("uniq_ID"="sample")) # add the data for lat lon

combined<-rbind(first50preds.l154[, c(1:2,13:15)], in16.rdg[,2:6])



# this next step allows for aggregation at any level by uniting the taxonomy at different levels
combined<-combined %>% 
  inner_join (run.list, by=c("zOTU" = "AMD_ID")) %>%
  unite("order_genus", c("Order", "Genus", "Species"), remove=F)
```

```{r, fig.width=8}
p3<-ggbarplot(combined, x= "lat", y = "value",  color = NA,  fill = "order_genus", palette=mycol,  size = 0.6, alpha = 1,legend = "right", orientation = "vertical")+ #position = position_dodge(1)
    font("xlab", size = 12, color = "blue")+ 
    facet_wrap(. ~ month.abb, drop=T, scales="free", nrow  =4)+ #scales="free"
   #facet_grid(cluster ~ loc, drop=T, scales="free") +
    font("ylab", size = 12, color = "#993333") +
    font("xy.text", size = 3, color = "black") +
    theme_tq() +theme(panel.spacing = unit(0.05, "cm"),  legend.text=element_text(size=4), 
        legend.key.size = unit(.4, "cm"),) + rotate_x_text(45) + scale_x_discrete()
  
  p3 + scale_x_discrete(breaks=seq(-50,0,10), labels=c(-50,-40,-30,-20,-10,0)) #+ theme(legend.position="none")

  
   #ggsave(filename =paste("~/tzline.realvspreds.154e.pdf", sep=""), width = 10, height=6)
```

There might be a significant difference betweeen the real conditions and the 'climatology' for that time of the year

get the satellite sst to compare - if possible plot the anomaly

```{r}
first.50.preds %>% filter(lat < -20, lat > -50, lon > 145, lon < 165) %>%
ggplot( aes(x = lon, y = lat, fill = temp))  + ylim(-50,-20) + xlim(145,165) +
    labs( x= "Longitude (˚E)", y="Latitude (˚N)", title = "CARS SST") +
    geom_tile() +
    scale_fill_gradientn(colours = oceColors9A(1026), na.value = NA) +
    geom_polygon(data = shore3, aes(x=long, y = lat, group = group), color = "NA", fill = "grey80") +
    theme_bw() +
    coord_fixed(1.3) +
    facet_wrap(. ~ month.abb) + theme_tq() + theme(panel.spacing = unit(0.05, "cm")) +theme(legend.position="right") + rotate_x_text(45)
ggsave(filename =paste("~/CARS.temp.by.month.alt.pdf", sep=""))
```

```{r}
clusters.sub<-read_csv("/Volumes/Monkey/Dropbox/zOTUs/TZ/output/tzpreds.latlonsub.csv")


mycol13<-c("#d8006d",
"#7a0036",
"#f3b9a6",
"#fbba59",
"#543e00",
"#b3d348",
"#becd8f",
"#2ca419",
"#003414",
"#008b62",
"#01aae2",
"#bd94ff",
"#ffa1d2")
clusters.sub<-clusters.sub %>%
  mutate("month.abb" =month.abb[month])
clusters.sub$month.abb<-as.factor(clusters.sub$month.abb)
clusters.sub$month.abb<-factor(clusters.sub$month.abb, levels=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "real data","Sep", "Oct", "Nov", "Dec"))


clusters.sub$cl500<-as.factor(clusters.sub$cl500)

clusters.sub %>%
 ggplot( aes(x = lon, y = lat, fill = cl500, color=cl500), )  + ylim(-45,-22) + xlim(145,155) +
   labs( x= "Longitude (˚E)", y="Latitude (˚N)", title = "Microbial provinces predicted from NRS + Voyage Data") +
   geom_point() +
   #scale_fill_discrete(palette = clusters.sub$cl500col, na.value = NA) +
   geom_polygon(data = shore3, aes(x=long, y = lat, group = group), color = "NA", fill = "grey80") +
   theme_bw() +
   coord_fixed(1.3) +
   facet_wrap(. ~ month.abb, nrow = 2) + theme_tq() + theme(panel.spacing = unit(0.05, "cm")) +theme(legend.position="right") + rotate_x_text(45) + scale_color_manual(values=mycol13) #clusters.sub$cl500col

ggsave(filename =paste("~/tz.bioregions.v1.pdf", sep=""), width = 15) 
```
Deepa supplied mapped coordinates for the actual in16t02 track. We can use these to extract the corresponding predictions

```{r}
in16.track<-read_csv("/Volumes/Monkey/Dropbox/zOTUs/TZ/output/tz_mapped_coord.csv")



in16.track<-in16.track %>% inner_join(first.50.preds, by=c("tzlon" = "lon"))



rowSums(sweep(in16.track[,15:62], 1, rowSums(in16.track[,15:62]), "/"))
in16.track.sweep<-cbind(in16.track[,1:14], sweep(in16.track[,15:62], 1, rowSums(in16.track[,15:62]), "/"))
head(in16.track.sweep)
in16.track<-in16.track.sweep[in16.track.sweep$tzlat==in16.track.sweep$lat,]
in16.track<-in16.track[in16.track$tzlat==in16.track$lat,]

in16.track.g<-in16.track %>% gather(zOTU, value,  c(15:62)) # convert to long format

in16.track.g<-in16.track.g[!duplicated(in16.track.g[,c("lat", "month", "zOTU")]),]


combined<-rbind(first50preds.l154[, c(1:2,13:15)], in16.rdg[,2:6])

p3<-ggbarplot(in16.track.g, x= "lat", y = "value",  color = NA,  fill = "zOTU", palette=rev(mycol49),  size = 0.6, alpha = 1,legend = "right", orientation = "vertical")+ #position = position_dodge(1)
    font("xlab", size = 12, color = "blue")+ 
    facet_wrap(. ~ month.abb, drop=T, nrow  =4)+ #scales="free"
   #facet_grid(cluster ~ loc, drop=T, scales="free") +
    font("ylab", size = 12, color = "#993333") +
    font("xy.text", size = 3, color = "black") +
    theme_tq() +theme(panel.spacing = unit(0.05, "cm"),  legend.text=element_text(size=4), 
        legend.key.size = unit(.4, "cm"),) + rotate_x_text(45) + scale_x_discrete()
  
  p3 + scale_x_discrete(breaks=seq(-50,0,10), labels=c(-50,-40,-30,-20,-10,0)) #+ theme(legend.position="none")

?sweep
```



work-up for model prediction loop below this line

```{r}
mycol320<-c("#ee0679", "#79003a", "#9d004d", "#f6b5c5", "#ff307c", "#ff5788", "#3a0014", "#d6c1c4", "#ff7c99",
 "#ffa9b7", "#78002d", "#ee0960", "#c2004c", "#920036", "#5a001c", "#b8003f", "#ff576f", "#c0003b",
 "#6c001d", "#fcb4b4", "#ff868a", "#940028", "#a20025", "#ff948f", "#fc3d4d", "#380400", "#540008",
 "#b80023", "#ffaca3", "#e4bdb7", "#e32e32", "#250900", "#ff6554", "#84000c", "#310d00", "#ff9179",
 "#540f00", "#fd5739", "#ffa58e", "#a20c00", "#b01900", "#861500", "#ff8058", "#621800", "#ff6334",
 "#e74f21", "#481600", "#fcb69d", "#ffa17c", "#692600", "#8c3300", "#9a3900", "#e15f06", "#cc5600",
 "#ff8834", "#efbb9b", "#984800", "#ffa057", "#a55400", "#331a00", "#ffb375", "#ff9b3a", "#7e4300",
 "#bb6a00", "#ff9a20", "#502d00", "#d48200", "#ffa730", "#ffb763", "#3e2600", "#7e5200", "#b37c00",
 "#f8bb50", "#5f4200", "#e4c18c", "#f5b309", "#8a6700", "#d09d00", "#eeb903", "#e4c27c", "#a68100",
 "#eec043", "#b38e00", "#e4c368", "#c4a000", "#292000", "#e0c645", "#cfc6ad", "#c5af00", "#6d6100",
 "#766b00", "#352f00", "#d5c77d", "#998e00", "#5c5600", "#d6c92d", "#c2b700", "#454400", "#969900",
 "#cdca68", "#cbc898", "#a7ae00", "#687000", "#525900", "#bdd129", "#7a7a79", "#bcd13d", "#6d8200",
 "#83a000", "#a7c918", "#bad060", "#b8cf7d", "#334a00", "#2a3e00", "#4e7300", "#91ca25", "#a2d64c",
 "#6dad00", "#5a9500", "#162100", "#386700", "#a7d473", "#abd286", "#418600", "#b7cda2", "#8fda56",
 "#6dc32d", "#bccab1", "#164900", "#7fdc54", "#299700", "#4fbd33", "#0d2e00", "#0c6300", "#2da921",
 "#9cd493", "#005111", "#00a22c", "#61df66", "#018b28", "#003c0c", "#004610", "#006c27", "#9fd3a3",
 "#01b64a", "#86d893", "#00c95a", "#30df6c", "#009d49", "#a5d1ad", "#2fe27c", "#00934c", "#00401e",
 "#41e08a", "#01985c", "#00b471", "#69dba0", "#017f50", "#002917", "#01df9d", "#76d9ad", "#007854",
 "#00cf94", "#00583e", "#00422e", "#01936d", "#00140d", "#00634f", "#00ba98", "#01a084", "#bbc9c5",
 "#018271", "#7ed6c4", "#37ddc5", "#001e1a", "#00352f", "#00baaa", "#005550", "#a3ceca", "#006a66",
 "#6bd7d3", "#00aeae", "#008182", "#69d6db", "#1fdaea", "#00373c", "#00848f", "#01a2b2", "#005f69",
 "#01c8dc", "#85d2df", "#01bedc", "#b9c9cf", "#01c5ed", "#003e4e", "#005368", "#019bc0", "#4acbff",
 "#03a8e1", "#016489", "#051118", "#004663", "#70c8ff", "#0ab7ff", "#a6caea", "#001e30", "#0286c3",
 "#4fb0ff", "#75baff", "#015b91", "#0174b9", "#003255", "#028deb", "#51a4ff", "#399eff", "#004274",
 "#9cbfff", "#0171c7", "#001631", "#004d91", "#87abff", "#016ad1", "#0a0e20", "#6c94ff", "#0169df",
 "#5086ff", "#c2c4df", "#002c6a", "#0046a7", "#005dde", "#003890", "#c2c1f7", "#c4c2ea", "#014ece",
 "#003699", "#00246f", "#0445c7", "#003bb5", "#000e40", "#baafff", "#a59aff", "#100a29", "#002999",
 "#988bff", "#0e0831", "#1826a4", "#040440", "#000d58", "#8066f0", "#9777ff", "#b494ff", "#00057a",
 "#481d9f", "#8754db", "#190234", "#9e61eb", "#d7bbf2", "#662db1", "#2d0064", "#7e3fc5", "#be7dff",
 "#d4a4ff", "#250040", "#3b0062", "#4d007b", "#d994ff", "#c568f1", "#a94cd3", "#de8cff", "#6c0094",
 "#eeb0ff", "#280031", "#a133b9", "#8c14a2", "#640072", "#d960e5", "#f986ff", "#fd9dff", "#500055",
 "#fb78fb", "#fbabf7", "#8f008c", "#d246c8", "#790073", "#dabed4", "#42003a", "#ef58d6", "#cc30b3",
 "#ff6edd", "#f3b2df", "#feade5", "#ff94e0", "#74005e", "#c20b9d", "#940076", "#e5bad5", "#e83eb9",
 "#ff77cf", "#b90086", "#ff5bc3", "#dc1d9e", "#600042", "#ff72c1", "#ff48b3", "#a1006a", "#390022",
 "#ff87c1", "#dd008b", "#83004e", "#bc006e", "#ff6aac", "#ff469f", "#54002c", "#ff5ea1", "#240311",
 "#940050", "#1c0910", "#ff96ba", "#ffa2bf", "#c10065")
```



```{r}
mycol<-c("#ff85ab", "#e4bcc2", "#260308", "#ba0040", "#ff6774", "#6b0018", "#ff826e", "#370e00", "#a33000",
 "#ffb088", "#512000", "#ff822d", "#bb6b00", "#ffb519", "#8c7c00", "#b5d122", "#5c7100", "#bdce83",
 "#aad372", "#193000", "#8dda50", "#48a300", "#00b04b", "#005e2f", "#4cde9f", "#00705e", "#002423",
 "#003752", "#0074b3", "#0194f9", "#a7c1ff", "#00519e", "#6c82ff", "#002467", "#120a28", "#011a80",
 "#6c40c5", "#2c078b", "#ac63ed", "#260039", "#892eb5", "#dd6df4", "#8e0088", "#fa63e0", "#ffa2dc",
 "#9f0070", "#ff51b6", "#a30060", "#ff4e97")


```




```{r}
write_csv(as.data.frame(d0tz.preds), "~/Dropbox/zOTUs/TZ/d0tz.pres.csv")
write_csv(as.data.frame(d0tz), "~/Dropbox/zOTUs/TZ/d0tz.csv")
write_csv(as.data.frame(d0cars.new), "~/Dropbox/zOTUs/TZ/d0cars.new.csv")
gmods.stats
gmods.rds.names
gmods.name
gmods.contributions
gmods.md
gmods.cm


gmods.names$value[i]
load(paste(path, gmods.names$value[i], sep=""))


corr.mean<-c(AMD_B16Sv1_3_zOTU_40611.mod[['cv.statistics']][['correlation.mean']], AMD_B16Sv1_3_zOTU_47475.mod[['cv.statistics']][['correlation.mean']], AMD_B16Sv1_3_zOTU_39005.mod[['cv.statistics']][['correlation.mean']])
dev.mean<-c(AMD_B16Sv1_3_zOTU_40611.mod[['cv.statistics']][['deviance.mean']], AMD_B16Sv1_3_zOTU_47475.mod[['cv.statistics']][['deviance.mean']], AMD_B16Sv1_3_zOTU_39005.mod[['cv.statistics']][['deviance.mean']])
contributions<-cbind(AMD_B16Sv1_3_zOTU_40611.mod[['contributions']][c("temp", "sal", "depth", "nox", "po4", "sil","n.p","strat", "DL"),2], AMD_B16Sv1_3_zOTU_47475.mod[['contributions']][c("temp", "sal", "depth", "nox", "po4", "sil","n.p","strat", "DL"),2], AMD_B16Sv1_3_zOTU_39005.mod[['contributions']][c("temp", "sal", "depth", "nox", "po4", "sil","n.p","strat", "DL"),2])

rownames(contributions)<-("temp", "sal", "depth", "nox", "po4", "sil","n.p","strat", "DL")
colnames(contributions)<-c("zOTU_40611", "zOTU_47475", "zOTU_39005")
stats<-rbind(contributions, corr.mean, dev.mean)
stats
rownames(stats)<-c("temp", "sal", "depth", "nox", "po4", "sil","n.p","strat", "DL", "correlation.mean", "deviance.mean")

kable(stats)
```



```{r}
plot(mod5, what = "density", type="persp", col=rev(oceColors9A(21420)), lwd=0.01)

dim(mod5$z)
```

Get mode statistics, contributions etc. 


```{r}
library(gplots)
rownames(contributions)<-contributions$.id
heatmap.2(as.matrix(contributions[,-1]), trace = "none", col=c("white", rev(oce.colorsViridis(99))), labRow = contributions$.id)
?heatmap.2


contributions.g<-gather(contributions, 'var',"value", -.id)
contributions.g
p <-ggplot(contributions.g,aes(.id,var,fill=value), orientation="vertical")+
geom_tile(color= "white",size=0.1, ) +
scale_fill_viridis_c(direction = -1, name="contributions") 
p + theme_tq() + theme(axis.text.x=element_text(angle=45,hjust=1)) 

p
```

```{r}
models.g.list<-mget(ls(pattern="my.mod.mm_b16s_mm_b16s_.......p"))
contributions<-lapply(models.g.list, function(x) x[['contributions']])
#library(plyr)
df<-ldply(contributions)
contributions<-spread(df, var,rel.inf )

cv.stats<-lapply(models.g.list, function(x) x[['cv.statistics']][['correlation.mean']])
cv.df<-ldply(cv.stats)
cv.stats.dm<-lapply(models.g.list, function(x) x[['cv.statistics']][['deviance.mean']])
cv.df.dm<-ldply(cv.stats.dm)

colnames(cv.df)<-c("mod","corr.mean", "mod", "dev.mean")
write_csv(cv.df, 'cv.mean.csv')
contributions<-read_csv("~/Dropbox/zOTUs/TZ/gauss.contributions.csv")


```


```{r}
load("/Volumes/LaCie/BRT_2018/tz_models_210618_DRV/AMD_B16Sv1_3_zOTU_174826.gaussian.RData")
saveRDS(my.mod, "/Volumes/LaCie/BRT_2018/tz_models_210618_DRV/AMD_zOTU_174826.RDS")


d0cars.new<-read_csv("/Volumes/Monkey/Dropbox/zOTUs/TZ/d0cars.new.csv")

d0cars.new$month.abb<-as.factor(d0cars.new$month.abb)
d0cars.new$month.abb<-factor(d0cars.new$month.abb, levels=c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))


AMD_zOTU_174826<-readRDS("/Volumes/LaCie/BRT_2018/tz_models_210618_DRV/AMD_zOTU_174826.RDS")
mod<-AMD_zOTU_174826

AMD_zOTU_171212<-readRDS("/Volumes/LaCie/BRT_2018/tz_models_210618_DRV/AMD_zOTU_171272.g.RDS")



AMD_zOTU_171314<-readRDS("/Volumes/LaCie/BRT_2018/tz_models_210618_DRV/AMD_zOTU_171314.g.RDS")
                         
                         mod<-AMD_zOTU_171314
tmp<-predict.gbm(mod, d0cars.new, n.trees=mod[[28]][[15]], type="response")
tmp<-tmp^2
temp<-cbind(d0cars.new[,c(1:3, 13)], as.numeric(tmp))
colnames(temp)[5]<-"abundance"


ggplot(temp, aes(x = lon, y = lat, fill = abundance))  + ylim(-55,0) + xlim(90,180) +
    labs( x= "Longitude (˚E)", y="Latitude (˚N)", title = paste(mod[[28]][[5]], sep="")) +
    geom_raster(interpolate = TRUE) +
    scale_fill_gradientn(colours = c("white", rev(oceColorsTemperature(1026))), na.value = NA) +
    geom_polygon(data = shore3, aes(x=long, y = lat, group = group), color = "NA", fill = "grey80") +
    theme_bw() +
    coord_fixed(1.3) +
    facet_wrap(. ~ month.abb) + theme_tq() + theme(panel.spacing = unit(0.05, "cm")) +theme(legend.position="right")
ggsave(filename =paste("/Volumes/Monkey/",mod[[28]][[5]], ".g.local.pdf", sep=""))

ggplot(temp, aes(x = lon, y = lat, fill = abundance))  + ylim(-65,15) + 
    labs( x= "Longitude (˚E)", y="Latitude (˚N)", title = paste(mod[[28]][[5]], sep="")) +
    geom_raster(interpolate = TRUE) +
    scale_fill_gradientn(colours = c("white", rev(oceColorsTemperature(1026))), na.value = NA) +
    geom_polygon(data = shore3, aes(x=long, y = lat, group = group), color = "NA", fill = "grey80") +
    theme_bw() +
    coord_fixed(1.3) +
    facet_wrap(. ~ month.abb) + theme_tq() + theme(panel.spacing = unit(0.05, "cm"),) +theme(legend.position="right")
ggsave(filename =paste("/Volumes/Monkey/",mod[[28]][[5]], ".g.global.pdf", sep=""))


```

Import deepa's clusters and plot

```{r}
clusters.sub<-read_csv("~/Dropbox/zOTUs/TZ/output/tzpreds.latlonsub.csv")


mycol13<-c("#d8006d",
"#7a0036",
"#f3b9a6",
"#fbba59",
"#543e00",
"#b3d348",
"#becd8f",
"#2ca419",
"#003414",
"#008b62",
"#01aae2",
"#bd94ff",
"#ffa1d2")

mycol14<-c("#00242e",
"#f1b7c1",
"#aecfa9",
"#007b77",
"#4d4500",
"#004488",
"#9ad67d",
"#53dda6",
"#318800",
"#8c008d",
"#ff594d",
"#ff48a0",
"#f4a000")

in16.points<-read_csv("~/Dropbox/zOTUs/TZ/output/tz.real.md.csv")

clusters.sub$cl500<-as.factor(clusters.sub$cl500)

p<-ggplot(data=clusters.sub, aes(x = lon, y = lat, fill = cl500, color="NA"), )  + ylim(-45,-5) + xlim(145,155) +
    labs( x= "Longitude (˚E)", y="Latitude (˚N)", title = "Dynamic microbial provinces predicted from NRS + Voyage Data") +
    geom_tile() +
    #scale_fill_discrete(palette = clusters.sub$cl500col, na.value = NA) +
    geom_polygon(data = shore3, aes(x=long, y = lat, group = group), color = "NA", fill = "grey80") +
    theme_bw() +
    coord_fixed(1) +
    facet_wrap(. ~ month, nrow = 2) + theme_tq() + theme(panel.spacing = unit(0.05, "cm"),legend.text=element_text(size=18), 
        legend.key.size = unit(.5, "cm")) +theme(legend.position="right") + rotate_x_text(45) + scale_fill_manual(values=mycol14) + guides(colour = guide_legend(override.aes = list(size=10)))#clusters.sub$cl500col

p <- p+ geom_point(data=in16.points, aes(x=tz.real.lon, y=tz.real.lat), size=0.5, color="black", fill="NA") 

p

ggsave(filename =paste("~/tz.bioregions.v5.pdf", sep=""), width = 14) 

edit(theme_tq)
```

```{r}
write.table(in16.points)
in16.points$tz.real.lat[14]<--38.926
```

